A thesis draft

### 2018-11-22 res/sections/15-ArchitecturalImplementation.tex
Start the architectural implementation

>>>>

In this chapter we will dig into the actual architectural implementation, 
seeing all the problems related to it and how they were solved.

\section{Adopting Openstack for container orchestration}

Our first step was to try to use Openstack to create a container orchestration. 
The reason behind this approach was simple: Openbaton, on paper, provides an 
out-of-the-box support for Openstack. In fact, it natively supports Openstack 
PoPs, giving to us a great possibility to reuse the two frameworks and to ease 
the development phase of our software.
\subsection{Openstack for developers: Devstack}
% TODO talk about Devstack installation
